Supplementary Information

### 2021-04-27 doc/manuscript/Dow_manuscript_Nature.Rmd
archived old version

###~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## some stats/ 
species_table <- read.csv(file = "tables_figures/species_table.csv")
n_dendro_trees <- sum(na.omit(species_table[, "n.trees"]))
n_tree_years <- sum(na.omit(species_table[, "n.tree.years"]))
n_cores_focal_sites <- sum(na.omit(species_table[, "n.cores"]))
n_chronologies <- NA
n_cores_sites <- NA
n_chronologies_SCBI <- NA
n_chronologies_HF <- NA
```

@@

# Supporting Information

>>>>

###~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## some stats/ 
species_table <- read.csv(file = "tables_figures/species_table.csv")
n_dendro_trees <- sum(na.omit(species_table[, "n.trees"]))
n_tree_years <- sum(na.omit(species_table[, "n.tree.years"]))
n_cores_focal_sites <- sum(na.omit(species_table[, "n.cores"]))

#copy over chronologies table
chronologies_table <- read.csv(file ="tables_figures/chronology_table.csv")
n_chronologies <- nrow(chronologies_table) 
n_cores_sites <- NA
n_chronologies_SCBI <- NA
n_chronologies_HF <- NA
```

@@

# Additional Information

*Supplementary Information* is available for this paper.

Correspondence and requests for materials should be addressed to Kristina Anderson-Teixeira (teixeirak@si.edu).
